---
title: "Fitting Mixtures of Skew-t distributions to transformed p-values"
output:
  pdf_document: default
  html_notebook: default
---

```{r echo=F, cache=TRUE}
library(EMMIXcskew)
library(EMMIXskew)
library(ggplot2)
library(mnormt)
library(locfdr)
library(qvalue)
library(cepp)
library(mixtools)
library(knitr)
```

```{r, include=F}
source("density.R")
source("fit.R")
source("util.R") 


source("./misc/fmcfust.R")
source("./misc/fmmst.R")
source("./misc/fmcfust.R")

```
#Data

```{r echo=F,cache=TRUE}
data("hedenfalk")
hedenfalk$z<-qnorm(1-hedenfalk$p)
data("Colon")

for(i in 1:2000){
  Colon$t[i]<-t.test( Colon$X[Colon$Y==1,i] , Colon$X[Colon$Y==2,i] )$statistic
}
Colon$p<-pt(Colon$t,60)
Colon$z<-qnorm(1-Colon$p)

data("hivdata")# already pval
```


#Fit Mixture of 2 Normals
As in orginal paper.

```{r echo=F, plot.show='hold', cache=TRUE}
hiv_fit_norm <- normalmixEM(x=hivdata, lambda =pi_0(hivdata,3), k=2, maxrestarts=100)
hed_fit_norm <- normalmixEM(x=hedenfalk$z,k=2, lambda = pi_0(hedenfalk$z,0), mean.constr = c(0, NA), sd.constr=c(1, NA), maxrestarts=100) 
col_fit_norm <- normalmixEM(x=Colon$z, lambda =pi_0(Colon$z,0), k=2, mean.constr = c(0, NA), sd.constr=c(1, NA), maxrestarts=100)

plot_normal_densities(hiv_fit_norm,hivdata, 1000, 50, "Hiv Emp. Normal")
plot_normal_densities(col_fit_norm,Colon$z, 1000, 50, "Colon Normal")
plot_normal_densities(hed_fit_norm,hedenfalk$z, 1000, 50, "Hedenfalk Normal")
```
```{r echo=F, results='asis'}
kable(FDR_table(namer(hiv_fit_norm),c(seq(0.01, 0.1, 0.01))), caption="Estimated FDR and other Error rates for HIV")
```
```{r echo=FALSE, results = 'asis'}
kable(FDR_table(namer(hed_fit_norm),c(seq(0.1, 0.5, 0.1))),caption="Estimated FDR and other Error rates for Hedenfalk")
```
```{r, echo=F, results='asis'}
kable(FDR_table(namer(col_fit_norm),c(seq(0.1, 0.5, 0.1))),caption="Estimated FDR and other Error rates for Colon Cancer")
```

# Fit mixture of skew t-distributions

## Empirical mean
```{r echo=F, plot.show='hold', cache=TRUE}
hiv_fit <- fmcfust(2, hivdata, initial =list(pro=pi_0(hivdata,3)))
hed_fit <- fmcfust(2, hedenfalk$z,initial =list(pro=pi_0(hedenfalk$z,0)))
col_fit <- fmcfust(2, Colon$z,initial =list(pro=pi_0(Colon$z, 0)))

plot_skew_densities(col_fit , Colon$z, 1000, 50, "Colon Skew")
plot_skew_densities(hiv_fit , hivdata, 1000, 50, "HIV Skew")
plot_skew_densities(hed_fit , hedenfalk$z, 1000, 50, "Hedenfalk Skew")
```

```{r, echo=F, results='asis'}
kable(FDR_table(FDR_etc(namer(hiv_fit),0.1), caption="Mixture of skew t - HIV"))
```

```{r, echo=F, results='asis'}
kable(FDR_table(FDR_etc(namer(hed_fit),0.1), caption="Mixture of skew t - Hedenfalk"))
```

```{r, echo=F, results='asis'}
kable(FDR_table(FDR_etc(namer(col_fit),0.1), caption="Mixture of skew t - Colon Cancer"))
```

# Fit mixture of one skew t-distribution and one normal.
```{r echo=F, plot.show='hold', cache=TRUE}
hiv_fit_new<-fmcfust2((hivdata),3, verbose=T, emp=T)
plot_skew_norm_densities(hiv_fit_new , hivdata, 1000, 50, "HIV Skew/Norm")
```

```{r, echo=F, results='asis'} 
kable(FDR_table(namer(hiv_fit_new),0.1), caption="HIV Skew/Norm")
```

#partly free fits
#theoretocal null
```{r echo=F, plot.show='hold', cache=TRUE}
hed_fit_new<-fmcfust2(hedenfalk$z,1, verbose=T, emp=F)
plot_skew_norm_densities(hed_fit_new , hedenfalk$z, 1000, 50, "Hedenfalk Skew/Norm")
```

```{r, echo=F, results='asis'} 
kable(FDR_table(namer(hed_fit_new),0.1), caption="Hedenfalk Skew/Norm")
```
# hiv_fit_new<-fmcfust2(hivdata,3, verbose=T, emp=F, g=3)
# plot_skew_densities3(hiv_fit_new , hivdata, 1000, 50, "HIV Skew/Norm")
# FDR_etc(namer(hiv_fit_new),0.1)

col_fit_new<-fmcfust2(Colon$z,1, verbose=T, emp=F)
plot_skew_norm_densities(col_fit_new , Colon$z, 1000, 50, "Colon Skew/Norm")
```{r, echo=F, results='asis'} 
kable(FDR_table(namer(col_fit_new),0.1), caption="Colon Skew/Norm")
```

# Some BIC and AIC values

```{r}
2*(5)-2*col_fit_norm$loglik
col_fit$aic
col_fit_new$aic

2*(5)*log(length(col_fit_norm$x)) -2*col_fit_norm$loglik
col_fit$bic
col_fit_new$bic


2*(5)-2*hiv_fit_norm$loglik
hiv_fit$aic
hiv_fit_new$aic

2*(5)*log(length(hiv_fit_norm$x)) -2*hiv_fit_norm$loglik
hiv_fit$bic
hiv_fit_new$bic



2*(5)-2*hed_fit_norm$loglik
hed_fit$aic
hed_fit_new$aic

2*(5)*log(length(hed_fit_norm$x)) -2*hed_fit_norm$loglik
hed_fit$bic
hed_fit_new$bic


```


